%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis Typographic Thesis
% LaTeX Template
% Version 1.3 (15/2/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% André Miede (http://www.miede.de)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% General Tips:
% 1) Make sure to edit the classicthesis-config.file
% 2) New enumeration (A., B., C., etc in small caps): \begin{aenumerate} \end{aenumerate}
% 3) For margin notes: \marginpar or \graffito{}
% 4) Do not use bold fonts in this style, it is designed around them
% 5) Use tables as in the examples
% 6) See classicthesis-preamble.sty for useful commands
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
    twoside,openright,titlepage,numbers=noenddot,headinclude,%1headlines,
                footinclude=true,cleardoublepage=empty,
                BCOR=5mm,paper=a4,fontsize=11pt, % Binding correction, paper type and font size
                ngerman,english, % Languages
                ]{scrreprt}

% Includes the file which contains all the document configurations and packages - make sure to edit this file
\input{classicthesis-config}

\begin{document}

\frenchspacing % Reduces space after periods to make text more compact

\raggedbottom % Makes all pages the height of the text on that page

\selectlanguage{english} % Select your default language - e.g. american or german

%\renewcommand*{\bibname}{new name} % Uncomment to change the name of the bibliography
%\setbibpreamble{} % Uncomment to include a preamble to the bibliography - some text before the reference list starts

\pagenumbering{roman} % Roman page numbering prior to the start of the thesis content (i, ii, iii, etc)

\pagestyle{plain} % Suppress headers for the pre-content pages

%----------------------------------------------------------------------------------------
%	PRE-CONTENT THESIS PAGES
%----------------------------------------------------------------------------------------

\include{FrontBackMatter/Titlepage} % Main title page

\include{FrontBackMatter/Titleback} % Back of the title page

\cleardoublepage\include{FrontBackMatter/Dedication} % Dedication page

%\cleardoublepage\include{FrontBackMatter/Foreword} % Uncomment and create a Foreword.tex to include a foreword

\cleardoublepage\include{FrontBackMatter/Abstract} % Abstract page
\cleardoublepage\include{FrontBackMatter/AbstractDE} % Abstract page

% \cleardoublepage\include{FrontBackMatter/Publication} % Publications from the thesis page

% \cleardoublepage\include{FrontBackMatter/Acknowledgments} % Acknowledgements page

\pagestyle{scrheadings} % Show chapter titles as headings

\cleardoublepage\include{FrontBackMatter/Contents} % Contents, list of figures/tables/listings and acronyms

\cleardoublepage

\pagenumbering{arabic} % Arabic page numbering for thesis content (1, 2, 3, etc)
%\setcounter{page}{90} % Uncomment to manually start the page counter at an arbitrary value (for example if you wish to count the pre-content pages in the page count)

\cleardoublepage % Avoids problems with pdfbookmark

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - CHAPTERS
%----------------------------------------------------------------------------------------

% -------------------------------------------------------
% THE NEDM EXPERIMENT
% -------------------------------------------------------
\ctparttext{
An existence of an electric dipole moment of the neutron breaks fundamental symmetries of nature and, thereby, gives insight into big problems of contemporary physics. For example the dominance of matter over antimatter in the Universe. Its discovery is constantly pursued since 1950s, the newest effort being conducted in the Paul Scherrer Institute in Switzerland. In the first part we explain how the measurement of the neutron electric dipole moment motivated the original work of the author, described in the two further parts of this thesis.}
\part{Neutron Electric Dipole Moment}
\include{Chapters/nedm_at_psi}
\include{Chapters/nedm_at_psi_apparatus}

% -------------------------------------------------------
% SFC DESIGN
% -------------------------------------------------------
\ctparttext{
Stability of the magnetic field is a major challenge in measurements of the electric dipole moment of the neutron. An active magnetic shielding system had been succesfully used already in the nEDM experiment. This part begins with a discussion of the principles of active magnetic shielding and a description of the nEDM's system.

Spatial constraints made the design of coils for an n2EDM active shield challenging. This motivated the development of a new method of magnetic field coil design, which is part of this work.

Further, a prototype of an active magnetic shield featuring coils designed with the new method is described. The system had an unprecedentedly large useful volume. It constructively showed, that an active magnetic shield for the n2EDM experiment could be built.

Finally, a magnetic field mapping device is presented. It was used to characterise the magnetic field on the n2EDM site, providing crucial input to the design of an active shield.
    
The developments described in Part II laid the foundation for an active magnetic shield for the n2EDM experiment, which would reduce the tens-of-microteslas variations down to just a few.
}
\part{Active Magnetic Shielding}
\include{Chapters/nedm_sfc}
\include{Chapters/coil_design}
\include{Chapters/sfc_prototype}
\include{Chapters/mapping}

% -------------------------------------------------------
% AXION SEARCH
% -------------------------------------------------------
\ctparttext{Most of the universe, an estimated \SI{84}{\percent}, is dark matter. Among candidates for its constituents is an ultra-low-mass axion. In this part a search for a signature of an axion dark matter in the data of the nEDM experiment at PSI is described. The ratio of the spin-precession frequencies of stored ultracold neutrons and ${}^{199}$Hg atoms was analysed for an axion-induced oscillating electric dipole moment of the neutron and an axion-wind spin-precession effect. No signal consistent with dark matter was observed for the axion mass range $\SI{e-24}{\electronvolt} \leq m_a \leq \SI{e-17}{\electronvolt}$. The null result set the first laboratory constraints on the coupling of axion dark matter to gluons, which improved on astrophysical limits by up to three orders of magnitude. It also improved on previous laboratory constraints on the axion coupling to nucleons by up to a factor of 40.

The first section in this part introduces the subject of axion-like dark matter. In the second the method of choice for the analysis, the least-squares periodogram, is discussed. The methodology developed there is then applied to the PSI nEDM dataset in the third section. The part concludes with a proposal for a resonant oscillating electric dipole moment.}
\part{Axion Dark Matter Search}
\include{Chapters/alp_intro}
\include{Chapters/alp_periodograms}
\include{Chapters/alp_analysis}
% \include{Chapters/alp_everything}
% \include{Chapters/alp_prx}


\cleardoublepage\include{Chapters/conclusion}

\cleardoublepage\include{FrontBackMatter/Acknowledgments} % Acknowledgements page

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - APPENDICES
%----------------------------------------------------------------------------------------

\appendix

\part{Appendix} % New part of the thesis for the appendix

% Let the appendices start on the left page, too.
\begingroup
\let\cleardoublepage\clearpage

% \include{Chapters/Chapter0A} % Appendix A
\include{Chapters/R_derivation_appendix}
\include{Chapters/sfc_appendix}
\include{Chapters/chalet_map_appendix}
\include{Chapters/remote_magnetometers_appendix}
\include{Chapters/alp_appendix}
\include{Chapters/caching_scheme_appendix}
% \include{Chapters/tools}
%\include{Chapters/Chapter0B} % Appendix B - empty template

\endgroup

%----------------------------------------------------------------------------------------
%	POST-CONTENT THESIS PAGES
%----------------------------------------------------------------------------------------

\cleardoublepage\include{FrontBackMatter/Bibliography} % Bibliography

% \cleardoublepage\include{FrontBackMatter/Colophon} % Colophon

% \cleardoublepage\include{FrontBackMatter/Declaration} % Declaration

%----------------------------------------------------------------------------------------

\end{document}
