\chapter{The most exciting observable}
\label{ch:nedm-at-psi}

antohe asonethu snthaoeu

Check out Ed Hind's talk he gave at ETH! I could make something around it.

Why are we here? Because of CP symmetry breaking! - Ed Hinds.
Need to explain the baryon-assymetry.

We expect something around the scale of the weak interaction, new particles.


Additionally, the strong CP problem!


citing from \emph{Electric dipole moments as probes of new physics}

All existing searches have failed to detect any intrin- sic EDM, and indeed the precision to which EDMs are now known to vanish is remarkable, and sufficient to render them some of the most important precision tests of the Standard Model. In this more general context, the strong CP problem, associated with the tuning of h, becomes just the most highly tuned example among many possible CP-odd operators which could contribute to the observable EDMs of nucleons, leptons, atoms, and molecules. Anticipating the presence of such CP-odd sources is not without motivation. Indeed, one of the strongest moti- vations comes from cosmology, where the success of the inflationary scenario, to- gether with the observed cosmological dominance of baryons over antibaryons, suggests that a non-zero baryon number was generated dynamically in the early Universe. According to the Sakharov criteria [8], this requires a source of CP-vio- lation, and within the Standard Model, neither the Kobayashi–Maskawa phase nor the h-term can create conditions that would lead to the generation of an apprecia- ble net baryon number. This strongly suggests the presence of another, yet to be discovered, source of CP-violation in nature. Although exceptions exist, e.g., the leptogenesis scenario, EDMs generally provide a highly sensitive diagnostic for these new CP-odd sources.